% options:
% thesis=B bachelor's thesis
% thesis=M master's thesis
% czech thesis in Czech language
% english thesis in English language
% hidelinks remove colour boxes around hyperlinks

\documentclass[thesis=M,english]{FITthesis}[2012/10/20]

% \usepackage[utf8]{inputenc} % LaTeX source encoded as UTF-8
% \usepackage[latin2]{inputenc} % LaTeX source encoded as ISO-8859-2
% \usepackage[cp1250]{inputenc} % LaTeX source encoded as Windows-1250

\usepackage{graphicx} %graphics files inclusion
% \usepackage{subfig} %subfigures
% \usepackage{amsmath} %advanced maths
% \usepackage{amssymb} %additional math symbols
\usepackage{dirtree} %directory tree visualisation
\usepackage{mathtools}
\usepackage{amsmath}
%\usepackage{commath}
\usepackage[colorinlistoftodos]{todonotes}
%\usepackage[colorlinks=true, allcolors=blue]{hyperref}
%\usepackage{standalone}
\usepackage{subcaption}
\usepackage{caption}

% % list of acronyms
% \usepackage[acronym,nonumberlist,toc,numberedsection=autolabel]{glossaries}
% \iflanguage{czech}{\renewcommand*{\acronymname}{Seznam pou{\v z}it{\' y}ch zkratek}}{}
% \makeglossaries
%\DeclarePairedDelimiter{\abs}{\lvert}{\rvert}
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
% EDIT THIS
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 

\department{Department of Knowledge Engineering}
\title{Approximate Pattern Matching In Sparse Multidimensional Arrays Using Machine Learning Based Methods}
\authorGN{Anna} %author's given name/names
\authorFN{Ku{\v c}erov{\' a}} %author's surname
\author{Anna Ku{\v c}erov{\' a}} %author's name without academic degrees
\authorWithDegrees{Bc. Anna Ku{\v c}erov{\' a}} %author's name with academic degrees
\supervisor{Ing. Lubo{\v s} Kr{\v c}{\' a}l}
\acknowledgements{Main credit goes to my supervisor Ing. Lubo{\v s} Kr{\v c}{\' a}l without whom this work could not be finished.}
\abstractEN{The main goal of this work is to propose a solution of approximate pattern matching with the use of machine learning based methods. This is done with the help of Locality Sensitive Hashing and Stricter Filter algorithm proposed by Navaro and Baeza-Yates. Previous work were focused primarily low dimensional pattern matching (1-2D). The outcome of this work is an algorithm together with time measures and comparison with already proposed solutions, where algorithms created by Navaro and Baeza-Yates were implemented for the first time, the solution also uses binary format used by SciDB. }
\placeForDeclarationOfAuthenticity{Prague}
%\keywordsCS{Replace with comma-separated list of keywords in Czech.}
\keywordsEN{Approximate Pattern Matching, Pattern Matching, Hash function, Stricter Filter, Fast Filter for Searching, SciDB, Data Chunking}
\declarationOfAuthenticityOption{1} %select as appropriate, according to the desired license (integer 1-6)
% \website{http://site.example/thesis} %optional thesis URL
\setcounter{tocdepth}{2}

\begin{document}
\nocite{*}
% \newacronym{CVUT}{{\v C}VUT}{{\v C}esk{\' e} vysok{\' e} u{\v c}en{\' i} technick{\' e} v Praze}
% \newacronym{FIT}{FIT}{Fakulta informa{\v c}n{\' i}ch technologi{\' i}}

\setsecnumdepth{part}

\input{introduction}

\input{analysis}

\input{implementation}

\input{results}

\input{conclusion}

\bibliographystyle{iso690}
\bibliography{bibliography}

\setsecnumdepth{all}
\appendix

\chapter{Acronyms}
% \printglossaries
\begin{description}
	\item[AFL] Array Functional Language
	\item[AMR] Adaptive Mesh Refinement
	\item[ANN] Approximate Nearest Neighbour
	\item[AQL] Array Query Language
	\item[BA] Brute Force solution of approximate pattern matching
	\item[BE] Brute Force solution of exact pattern matching
	\item[CSV] Comma Separated Values
	\item[DNA] Deoxyribonucleic Acid
	\item[EEG] Electroencephalogram
	\item[FFS] Fast Filter Searching for approximate pattern matching
	\item[HS] Naive Hashed Stricter Filter
	\item[HS1] Improved HS
	\item[HR] HS1 using different hash function
	\item[KMP] Knuth--Morris--Pratt
	\item[KNN] K Nearest Neighbours
	\item[KS] Krithivasan and Sitalakshmi
	\item[LSB] Least Significant Bit
	\item[LSH] Locality Sensitive Hashing
	\item[MAT] Medial Axis Transformation
	\item[RasDaMan] Raster Data Manager
	\item[RC] Row, Column
	\item[RNN] R-Near Neighbour
	\item[SBST] Self Balancing Binary Search Tree
	\item[SE] Baeza-Yates and Navarro solution of exact pattern matching
	\item[SF] Stricter Filter for approximate pattern matching
	\item[SQL] Structured Query Language	
\end{description}


\chapter{Contents of enclosed USB}

\begin{figure}
	\dirtree{%
		.1 readme.txt\DTcomment{the file with CD contents description}.
		.1 exe\DTcomment{the directory with executables}.
		.1 src\DTcomment{the directory of source codes}.
		.2 wbdcm\DTcomment{implementation sources}.
		.2 thesis\DTcomment{the directory of \LaTeX{} source codes of the thesis}.
		.1 text\DTcomment{the thesis text directory}.
		.2 thesis.pdf\DTcomment{the thesis text in PDF format}.
		.2 thesis.ps\DTcomment{the thesis text in PS format}.
	}
\end{figure}

\input{appendix}



\end{document}
